---
title: "MTurk data cleaning"
author: "Janet Xu"
date: "6/15/2018"
output: pdf_document
---

Code released under an MIT license.

# Step 1: rename variables, merge the two internet variables into one, recode smoking question into binary, delete apple pie attention check
```{r, message = F, warning = F echo = T}
# load packages
library(tidyverse)
library(caret)

## STEP 0: Done before downloading data:
#### A) Deleted responses that didn't pass attention check (n = 26)
#### B) Deleted duplicates (n = 11)
#### C) Deleted Worker ID, timestamp, and zip code variables


# load dirty data
setwd("~/Dropbox/SICSS/mturk_survey_2018/data")
data <- read.csv("mturk_anon.csv", header = TRUE, na.strings = c("NA",""))
## note: everything except age is stored as factors

# rename variables
## note: dependent variables are uppercase
colnames(data) <- c("attention1", 
                    "MILITARY",
                    "ECONUS",
                    "EDU",
                    "ENVIRON", 
                    "ECONINTL",
                    "HEALTH",
                    "HIGHWAY",
                    "SCIENCE",
                    "SOCIAL",
                    "GUNS",
                    "ISLAM",
                    "SATISFIED",
                    "GOVT",
                    "TRADE",
                    "attention2",
                    "sex",
                    "age",
                    "educ",
                    "hisp",
                    "race",
                    "state",
                    "SMOKING",
                    "LANDLINE",
                    "INTERNET1",
                    "INTERNET2",
                    "ideology",
                    "party1",
                    "party2")

# remove attention2 (apple pie question) because no variation -- 
# all incorrect responses screened out
data <- data %>% select(-attention2) %>%
# combine INTERNET1 and INTERNET2 the same way Pew does -- yes to EITHER counts
        mutate(INTERNET = as.factor(ifelse(INTERNET1 == "Yes" | INTERNET2 == "Yes",
                                           "Yes", "No"))) %>%
# then drop INTERNET1 and INTERNET2
        select(-INTERNET1, -INTERNET2) %>%
# collapse everyday smokers and some days smokers into current smoker category (to match Center for Diseases Control and Prevention definition)
        mutate(SMOKER = as.factor(ifelse(SMOKING == "Every day" | SMOKING == "Some days", 1, 2))) %>%
        select(-SMOKING)
    
head(data)
```

# Step 2a: make sure factor levels are in the same order as questionnaire

```{r}
# need to switch "decrease" and "increase" for all spending questions
# write a function for this
spending.function <- function(x){
  factor(x, levels = c("Increase spending",
                      "Decrease spending",
                      "Keep spending the same"))
  }
# apply
data[ ,2:10] <- lapply(data[ ,2:10], spending.function)

#check
levels(data$MILITARY)

# switch order of binary responses for binary ques
# write function
switch.function <- function(x){
  factor(x, levels = rev(levels(x)))
}
# apply function
data[ ,c("GUNS", "ISLAM", "SATISFIED", "GOVT", "TRADE", "LANDLINE", "INTERNET")] <-
 lapply(data[ ,c("GUNS", "ISLAM", "SATISFIED", "GOVT", "TRADE", "LANDLINE", "INTERNET")],
        switch.function)  

# check
levels(data$GUNS)
levels(data$ISLAM)
levels(data$SATISFIED)
levels(data$GOVT)
levels(data$TRADE)
levels(data$LANDLINE)
levels(data$INTERNET)
```


# Step 2b: binarization of dependent variables (aka one-hot encoding); for binary variables, just keep the first response


```{r}
# for dependent variables, convert factors to underlying numeric codes
data_num <- cbind(lapply(data[ ,c(2:15, 27, 22, 26)], as.numeric),
                  data[, c(1, 16:21, 23:25)])

# isolate dep vars and factorize again
ds.qid <- data_num[, 1:17]
ds.qid <- lapply(ds.qid, as.factor) 

# dummify
dmy <- dummyVars(" ~ .", data = ds.qid)
ds.qid.dmy <- data.frame(predict(dmy, newdata = ds.qid))

head(ds.qid.dmy)
## note, for example, that now MILTARY is MILTARY.1, MILITARY.2, MILITARY3, corresponding 
## to the three categories of the question

# merge the dummies back to dataset
ds <- cbind(data_num[ ,18:27], ds.qid.dmy)
head(ds)

# for the binary questions, remove the second option bc that is perfectly collinear
ds <- ds %>% select(-GUNS.2, -ISLAM.2, -SATISFIED.2, -GOVT.2, -TRADE.2, 
                    -SMOKER.2, -LANDLINE.2, -INTERNET.2)
```

# Step 3: recode race, make age into categories; add region

```{r}
# recode race
## note: there are many ways to code these data into mutually exclusive categories
## for simplicity's sake, everyone who checked multiple races is coded as "other",
## this is just one way to code it and not really the "right" way to deal with this data,
## and you are welcome/encouraged to try other ways
table(ds$race, ds$hisp)

ds$raceth <- ifelse(ds$hisp == "Yes", "hispanic",
                    ifelse(ds$race == "Black or African-American", "black",
                           ifelse(ds$race == "Asian or Asian-American", "asian",
                                  ifelse(ds$race == "White", "white", "other"))))

ds <- ds %>% select(-race, -hisp) %>% mutate(race = raceth) %>% select(-raceth)

# age into categories
ds <- ds %>% mutate(age_cat = ifelse(ds$age >= 18 & ds$age <= 29, "18 - 29", 
                   ifelse(ds$age >= 30 & ds$age <= 49, "30 - 49", 
                   ifelse(ds$age >= 50 & ds$age <= 64, "50 - 64", "65 +")))) %>%
             select(-age) 

# add region
northeast <- c("Connecticut", "Maine", "Massachusetts", "New Hampshire", "Rhode Island", 
               "Vermont", "New Jersey", "New York", "Pennsylvania")
midwest <- c("Illinois", "Indiana", "Michigan", "Ohio", "Wisconsin", "Iowa", "Kansas", 
             "Minnesota", "Missouri", "Nebraska", "North Dakota","South Dakota")
south <- c("Delaware", "Florida", "Georgia", "Maryland", "North Carolina", "South Carolina",
           "Virginia", "District of Columbia", "West Virginia", "Alabama", "Kentucky", 
           "Mississippi", "Tennessee", "Arkansas", "Louisiana", "Oklahoma", "Texas")

ds <- ds %>% mutate(region = ifelse(state %in% northeast, "Northeast",
                 ifelse(state %in% midwest, "Midwest",
                 ifelse(state %in% south, "South", "West")))) %>%
  # drop state and zip code for privacy
             select(-state)

  
```

# Step 4: save

```{r}
write.csv(ds, "cleaned_mturk_jun18_data.csv", row.names = F)

```
