---
title: "MTurk Data Cleaning"
author: "Cambria Naslund ^[based on code by Janet Xu for SICSS 2018]"
date: "6/13/2019"
output: html_document
---

# Step 1: Load MTurk survey data

### Before downloading data
- Dropped responses that did not select "I agree" on consent check (n=1)
- Dropped duplicates (n=2)
- Deleted MTurk worker ID, consent check, and timestamp variables

### Load data and tidy
- Download responses (as .csv) from Google Forms and load
- Rename variables (match names in Pew benchmark and cleaned ACS data)
- Delete responses that failed the apple pie attention check

```{r, message = F, warning = F, echo = T}
# load packages
library(tidyverse)
library(caret)

# load local data
setwd("local_data")
data <- read.csv("mturk_anon.csv", header = TRUE, na.strings = c("NA",""))
## n = 510
## note: all vars except age are stored as factors

# rename variables
## matching names with cleaned ACS and Pew benchmarks datasets
## note: dependent variables are uppercase
colnames(data) <- c("attention1",
                    "MILITARY",    
                    "ECONUS",
                    "EDU",
                    "ENVIRON", 
                    "ECONINTL",
                    "HEALTH",
                    "HIGHWAY",
                    "SCIENCE",
                    "SOCIAL",
                    "FEELGOV",
                    "DISCRIM",
                    "WORLDAFF",
                    "GOVTSIZE",
                    "SATISFIED",
                    "attention2",
                    "sex",
                    "age",
                    "educ",
                    "hisp",
                    "race",
                    "state",
                    "SMARTPHONE",
                    "INTERNET",
                    "PARTY",
                    "PARTYLN")

# remove incorrect responses for attention2 and drop variable
data <- data %>% filter(attention2 == "Somewhat approve") %>%
                 select(-attention2)
```

# Step 2: Change factor levels to match order in Pew questionnaire 

```{r}
# check order
levels(data$MILITARY)

# we need to switch "decrease" and "increase" for all spending questions
# write a function for this
spending.function <- function(x){
  factor(x, levels = c("Increase spending",
                      "Decrease spending",
                      "Keep spending the same"))
  }
# apply function to spending questions
data[ ,2:10] <- lapply(data[ ,2:10], spending.function)
# check
levels(data$MILITARY)

# fix levels for FEELGOV
data$FEELGOV <- factor(data$FEELGOV, levels = c("Content",
                                                "Frustrated",
                                                "Angry"))

# fix levels for SMARTPHONE
data$SMARTPHONE <- factor(data$SMARTPHONE, levels = c("Smartphone",
                                                      "Cell phone that is not a smartphone",
                                                      "No cell phone"))

# fix levels for PARTY
## note: "Don't know" is intentionally excluded here as Pew results collapse DK and Ref.
data$PARTY <- factor(data$PARTY, levels = c("Republican",
                                            "Democrat",
                                            "Independent",
                                            "No preference",
                                            "Other party"))

# switch levels of binary questions in the wrong order
# write function
switch.function <- function(x){
  factor(x, levels = rev(levels(x)))
}
# apply function
data[ ,c("DISCRIM", "GOVTSIZE","SATISFIED","INTERNET", "PARTYLN")] <-
 lapply(data[ ,c("DISCRIM","GOVTSIZE","SATISFIED","INTERNET", "PARTYLN")],
        switch.function)  

# check variables
levels(data$FEELGOV)
levels(data$DISCRIM)
levels(data$WORLDAFF)
levels(data$GOVTSIZE)
levels(data$SATISFIED)
levels(data$SMARTPHONE)
levels(data$INTERNET)
levels(data$PARTY)
levels(data$PARTYLN)
```

# Step 3: Binarize dependent variables (one-hot encoding)
Note: For questions with two response categories, only keep dummy variable for first category.

```{r}
# replace factor labels with underlying numerical codes
## isolate dependent variables and convert to numeric
data_dvs <- lapply(data[ ,c(2:15, 22:25)], as.numeric)
## convert back to factor
data_dvs <- lapply(data_dvs, as.factor)
levels(data_dvs$MILITARY)

# dummify
## note: these functions come from the caret package by Max Kuhn
dmy <- dummyVars(" ~ .", data = data_dvs)
data_dmy <- predict(dmy, newdata = data_dvs)
## note that MILITARY is now MILITARY.1, MILITARY.2, and MILITARY.3, corresponding 
## to each of the three options for that question
head(data_dmy[,1:8])

# merge new dummy vars with other variables from data
ds <- cbind(data_dmy, data[, c(1, 16:21)])

# for questions with only two options , drop dummy var for second category as it will be perfectly collinear
ds <- ds %>% select(-DISCRIM.2, -WORLDAFF.2, -GOVTSIZE.2, -SATISFIED.2, -INTERNET.2, -PARTYLN.2)

# check variables
# head(ds)
colnames(ds)
```

# Step 4: Recode responses from demographic questions to match variables in cleaned ACS data (race, age, region, education)

```{r}
# recode race
## note: there are many ways to code these data into mutually exclusive categories
## for simplicity's sake, everyone who checked multiple races is coded as "other",
## and hispanic is added as a separate category that includes everyone who selected yes
## this is just one way to code it and not really the "right" way to deal with this data,
## and you are welcome/encouraged to try other ways
table(ds$race, ds$hisp)
ds <- ds %>% mutate(race1 = ifelse(ds$hisp == "Yes", "hispanic",
                    ifelse(ds$race == "Black or African American", "black",
                           ifelse(ds$race == "Asian or Asian-American", "asian",
                                  ifelse(ds$race == "White", "white", "other")))))
ds <- ds %>% select(-race, -hisp) %>% mutate(race = race1) %>% select(-race1)


# age into categories
ds <- ds %>% mutate(age_cat = ifelse(ds$age >= 18 & ds$age <= 29, "18 - 29", 
                   ifelse(ds$age >= 30 & ds$age <= 49, "30 - 49", 
                   ifelse(ds$age >= 50 & ds$age <= 64, "50 - 64", "65 +")))) %>%
  #drop age for privacy
             select(-age) 


# collapse states into regions
northeast <- c("Connecticut", "Maine", "Massachusetts", "New Hampshire", "Rhode Island", 
               "Vermont", "New Jersey", "New York", "Pennsylvania")
midwest <- c("Illinois", "Indiana", "Michigan", "Ohio", "Wisconsin", "Iowa", "Kansas", 
             "Minnesota", "Missouri", "Nebraska", "North Dakota","South Dakota")
south <- c("Delaware", "Florida", "Georgia", "Maryland", "North Carolina", "South Carolina",
           "Virginia", "District of Columbia", "West Virginia", "Alabama", "Kentucky", 
           "Mississippi", "Tennessee", "Arkansas", "Louisiana", "Oklahoma", "Texas")
west <- c("Arizona", "Colorado", "Idaho", "New Mexico", "Montana", "Utah", "Nevada", "Wyoming", "Alaska", "California", "Hawaii", "Oregon", "Washington")
ds <- ds %>% mutate(region = ifelse(state %in% northeast, "northeast",
                 ifelse(state %in% midwest, "midwest",
                 ifelse(state %in% south, "south", 
                 ifelse(state %in% west, "west", NA))))) %>%
  # drop state for privacy
             select(-state)


# recode educ to match categories in cleaned ACS data
ds <- ds %>% mutate(educ = recode_factor(educ, "No schooling completed" = "no high school diploma", 
                                    "Nursery or Preschool through Grade 12 (no high school diploma)" = "no high school diploma", 
                                    "High school graduate (including GED or alternative credential)" = "high school graduate",
                                    "Some college or Associate's Degree (for example: AA, AS)" = "some college or associate's degree",
                                    "Bachelor's degree (for example: BA, BS)" = "bachelor's degree",
                                    "Postgraduate or professional degree, including Master's, Doctorate, medical, or law degree (for example: MA, MS, MEng, MEd, MSW, MBA, MD, DDS, DVM, LLB, JD, PhD, EdD)" = "postgraduate or professional degree"))
```

# Step 5: Save

```{r}
write.csv(ds, "2019-06-13_mturk_data_clean.csv", row.names = F)
```