---
title: "Non-probability-based Surveys in Practice"
author: Matthew Salganik and Cambria Naslund ^[based on the activities from SICSS 2017 (created by Matthew Salganik and Yo-Yo Chen) and SICSS 2018 (created by Matthew Salganik and Janet Xu).]
date: "Summer Institute in Computational Social Science 2019" 
output:
  html_document:
    df_print: paged
    toc: yes
---

```{r, echo=F}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Load packages and data

```{r, message = F, warning = F, echo = T }
# load packages
library(tidyverse)
library(lme4)

# set your working directory
# setwd("~/user/working_directory")

# load cleaned data file for survey results
data <- read.csv("https://github.com/compsocialscience/summer-institute/raw/master/2019/materials/day4-surveys/activity/2019-06-13_mturk_data_clean.csv")
## not using education or political attention check, so drop these vars
## (you can use these if you want!)
data <- data %>% select(-attention1, -educ)

## NOTE: if you are using your own survey results, you will need to 
## do some wrangling before you can match with the benchmark or acs data
## for a walkthrough, see https://github.com/compsocialscience/summer-institute/blob/master/2019/materials/day4-surveys/activity/mturk_data_cleaning.Rmd

# load external information -- in this case, population info
census <- read.csv("https://github.com/compsocialscience/summer-institute/raw/master/2019/materials/day4-surveys/activity/2017_acs_data_clean.csv")

# load pew benchmarks
pew <- read.csv("https://github.com/compsocialscience/summer-institute/raw/master/2019/materials/day4-surveys/activity/2019_pew_benchmark_data.csv", 
                col.names = c("qid", "label", "pew_estimate", "source"))
pew <- pew %>% select(qid, pew_estimate)
```

\newpage

# Approach 1: Simple means 

First, we'll just take the mean of the whole sample for each question. This approach doesn't use any post-stratification.

## 1.1) Calculate means

```{r}
# take the mean of survey responses in mturk data
## remove demographic variables (factor vars)
## get column means
mturk_means <- data %>% select(-sex, -race, -age_cat, -region) %>%
  summarise_all(~mean(., na.rm = T))

# reshape from wide to long
## with columns for questions (call this qid) and for mean
mturk_means <- mturk_means %>% gather(qid, mean)

# preview
head(mturk_means)
```

## 1.2) Plot estimated means against benchmarks

**Tip**: You will be making this type of plot each time you generate a new set of estimates, so it would be helpful to write a function for this.

```{r}

# merge mturk mean estimates with benchmark
mean_est <- inner_join(pew, mturk_means, by = c("qid"))
head(mean_est)

# make function for plot
plot_comparison <- function(est_table, method, caption){
  graph <-  ggplot(est_table, 
                   aes(x = pew_estimate, y = method)) + 
  geom_point() + 
  labs(x = "Estimates from Pew", y = caption) +
  scale_x_continuous(limits = c(0,1)) + 
  scale_y_continuous(limits = c(0,1)) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") + 
  coord_fixed()
  return(graph)
}  

# plot
plot_comparison(est_table = mean_est, 
                method = mean_est$mean, 
                caption = "Non-weighted estimates from MTurk")

```

## 1.3) Plot distribution of estimation-benchmark differences 

**Tip**: You will also be making this type of plot each time you generate a new set of estimates, so it would be helpful to write a function for this as well.

```{r}
# calculate difference
mean_est$diff <- abs(mean_est$mean - mean_est$pew_estimate)

# function for plotting difference
plot_diff <- function(est_table){
  diff_graph <- ggplot(est_table, aes(x = diff)) + 
  geom_histogram(aes(y = (..count..)/sum(..count..)), binwidth = .025, 
                 colour = "black", fill = "white") + 
  theme_bw() + 
  geom_vline(aes(xintercept = median(diff)), linetype = "longdash") + 
  labs(x = "absolute difference", y = "density") + 
  scale_y_continuous(limits = c(0, 0.45)) 
  return(diff_graph)
}

# plot
plot_diff(mean_est)
```

\newpage

# Approach 2: Means with post-stratification (8 groups)

## 2.1) Calculate group means, group weights, and weighted means

To start, group by sex and region only. This should give you 8 groups (2 sexes by 4 regions).

Group weights can be calculated as $\frac{N_{h}}{N}$. They should sum to 1. You will need to calculate these group weights for the other approaches as well. 

```{r}
# get total census population
N <- sum(census$POP)

# calculate group weights 
## group population data by sex and region,
## get the sum for each cell and divide by total pop
population_counts <- census %>% 
  group_by(sex, region) %>%
  summarise(group_weight = sum(POP)/N)

# check that weights sum to one
if (sum(population_counts$group_weight) != 1) {
  print("weights don't sum to one")
}

head(population_counts)

# calculate group means for each question response
## group data by sex and region
## remove non-numeric variables (demographic vars)
## calculate group means for each column
sample_counts <- data %>%
  group_by(sex, region) %>% 
  select_if(is.numeric) %>%
  summarise_all(list(~mean(.,na.rm = T)))

# preview -- scroll for more columns
head(sample_counts)

# check that there are no empty cells
if (nrow(sample_counts) < nrow(population_counts)) {
  print("GROUPS MISSING:")
  print(nrow(population_counts) - nrow(sample_counts))
}

# merge population counts with sample counts
# left join and retain all groups in population
cell_based <- left_join(population_counts, 
            sample_counts, 
            by = c("sex", "region"))

# reshape wide to long
cell_based_long <- cell_based %>% gather(qid, mean, 
                                         -c(sex, region, group_weight),
                                         na.rm = F)

head(cell_based_long)

# multiply the group means and group weights in the cell_based_long dataframe 
# and call this weighted_mean
cell_based_long <- mutate(cell_based_long, weighted_mean = group_weight*mean)

# sum weighted means, grouping by question
mturk_cell_est <- cell_based_long %>% 
  group_by(qid) %>%
  summarise(mturk_cell_estimate = sum(weighted_mean, na.rm = T))


head(mturk_cell_est)
```

## 2.2) Plot estimated means against benchmarks

```{r}
# merge mturk cell-based weighted estimates with benchmark
simple_cell_est <- inner_join(pew, mturk_cell_est, by = c("qid"))
head(simple_cell_est)

# plot (you can use the function we created above)

```

## 2.3) Plot distribution of estimation-benchmark differences

```{r}
#calculate difference


#plot

```


\newpage

# Approach 3: Means with post-stratification (160 groups) and missing group imputation

## 3.1) Calculate group means, group weights, and weighted means

Can you get better estimates grouping by more variables? Try grouping on sex, region, age group, and race. 

You will now have 160 groups (2 x 4 x 5 x 4). Some of groups may be missing from your sample (e.g. 50-64 year old black women in the midwest). If a group is missing, their answers will automatically be treated as "zero" when computing weighted means. As a result, some question responses may be underestimated. One way to deal with this is to impute the missing values with the sample average for that variable (aka the simple means we calculated in the first step). You will do this in the next step. 

First, calculate the new group means, group weights, and weighted means as you did above in Approach 2. 

```{r}
# calculate group means, group weights, and weighted means


```

### 3.1.1) Dealing with missing groups: imputing with sample means

Now, replace the missing groups with the sample means you computed in 1.1. 

```{r}
# replace missing group means with sample means

```

## 3.2) Plot estimated means against benchmarks

Plot both your new group means and the estimated means against the Pew benchmarks. 

```{r}
################################## WITH NO IMPUTATION ###################################


################################## WITH IMPUTATION ######################################


```


## 3.3) Plot distribution of estimation-benchmark differences

```{r}
#################################### WITH NO IMPUTATION #################################


#################################### IMPUTATION #######################################


```

\newpage

# Approach 4: Model-based estimation with post-stratification

## 4.1) Predict group means with simple regression model; combine with group weights to create weighted means

```{r}


```

## 4.2) Plot estimated means against benchmarks

```{r}


```

## 4.3) Plot distribution of estimation-benchmark differences 

```{r}



```


\newpage

# Compare distribution of differences across methods and questions

Which questions worked well and which didn't? Which methods worked well for which questions?

```{r}


```

\newpage

# Optional Extension -- Approach 5: Multilevel-Model-based estimation with post-stratification (MRP)

### 5.1) Predict group means with multi-level regression model; combine with group weights to create weighted means

```{r}


```

### 5.2) Plot estimated means against benchmarks

```{r}



```

### 5.3) Plot distribution of estimation-benchmark differences

```{r}



```

### 5.4) Compare differences from MRP with other methods

```{r}


```
