---
title: "Non-probability-based Surveys in Practice"
author: Matthew Salganik and Lai Wei ^[based on the activities from SICSS 2017 - 2020 with input from Matthew Salganik, Yo-Yo Chen, Janet Xu, Cambria Naslund, and Robin Lee).]
date: "Summer Institute in Computational Social Science 2021" 
output:
  html_document:
    df_print: paged
    toc: yes
---

```{r, echo=F}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Load packages and data

```{r, message = F, warning = F, echo = T }
# load packages
library(tidyverse)
library(lme4)
# set your working directory
# setwd("~/user/working_directory")
# load cleaned data file for survey results
data <- read_csv("https://raw.githubusercontent.com/compsocialscience/summer-institute/master/2021/materials/day4-surveys/activity/2021_clean_mturk_data.csv")
# load external information -- in this case, population info
census <- read_csv("https://raw.githubusercontent.com/compsocialscience/summer-institute/master/2021/materials/day4-surveys/activity/2019_acs_data_clean.csv")
# load pew benchmarks

pew <- read_csv("https://raw.githubusercontent.com/compsocialscience/summer-institute/master/2021/materials/day4-surveys/activity/pew_benchmark_2021.csv")

# You can find more info about the pew benchmark under "source" and "label" variable, which we will drop in the analysis.

pew <- pew %>% dplyr::select(qid, pew_estimate)

# add one variable that denotes the group the question belongs
pew[1:11,"type"] <- "media"
pew[12:30,"type"] <- "priority"

```

\newpage

# Approach 1: Simple means 

First, we'll just take the mean of the whole sample for each question. This approach doesn't use any post-stratification.

## 1.1) Calculate means

```{r}
# take the mean of survey responses in mturk data
## remove demographic variables (factor vars)
## get column means
mturk_means <- data %>% dplyr::select(-sex, -race, -age_cat, -region) %>%
  summarise_all(~mean(., na.rm = T)) %>%
## reshape from wide to long using tidyr package
## with columns for questions (call this qid) and for mean 
## having the data in long format makes it easier to merge with the pew estimate for plotting figure 1
  pivot_longer(twitter:da, names_to = "qid", 
               values_to = "mean")
# preview
head(mturk_means)
```

## 1.2) Plot estimated means against benchmarks

**Tip**: You will be making this type of plot each time you generate a new set of estimates, so it would be helpful to write a function for this.

```{r}
# merge mturk mean estimates with benchmark
mean_est <- inner_join(pew, mturk_means, by = c("qid"))
head(mean_est)
# make function for plot
plot_comparison <- function(est_table, method, caption){
  graph <-  ggplot(est_table, 
                   aes(x = pew_estimate, y = method)) + 
  geom_point(aes(color = type)) + 
  labs(x = "Estimates from Pew", y = caption) +
  scale_x_continuous(limits = c(0,1)) + 
  scale_y_continuous(limits = c(0,1)) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") + 
  coord_fixed()
  return(graph)
}  
# plot
plot_comparison(est_table = mean_est, 
                method = mean_est$mean, 
                caption = "Non-weighted estimates from MTurk")
```

## 1.3) Plot distribution of estimation-benchmark differences 

**Tip**: You will also be making this type of plot each time you generate a new set of estimates, so it would be helpful to write a function for this as well.

```{r}
# calculate difference
mean_est$diff <- abs(mean_est$mean - mean_est$pew_estimate)
# function for plotting difference
plot_diff <- function(est_table){
  diff_graph <- ggplot(est_table, aes(x = diff)) + 
  geom_histogram(aes(y = (..count..)/sum(..count..),fill=type), binwidth = .025, 
                 colour = "black") + 
  theme_bw() + 
  geom_vline(aes(xintercept = median(diff)), linetype = "longdash") + 
  labs(x = "absolute difference", y = "density") + 
  scale_y_continuous(limits = c(0, 0.45)) 
  return(diff_graph)
}
# plot
plot_diff(mean_est)
```

\newpage

# Approach 2: Means with post-stratification (8 groups)

## 2.1) Calculate group means, group weights, and weighted means

To start, group by sex and region only. This should give you 8 groups (2 sexes by 4 regions).

Group weights can be calculated as $\frac{N_{h}}{N}$. They should sum to 1. You will need to calculate these group weights for the other approaches as well. 

```{r}
# get total census population

# calculate group weights 
## group population data by sex and region,
## get the sum for each cell and divide by total pop




# calculate group means for each question response
## group data by sex and region
## remove non-numeric variables (demographic vars)
## calculate group means for each column


# preview -- scroll for more columns


# check that there are no empty cells


# merge population counts with sample counts
# left join and retain all groups in population


# reshape wide to long



# multiply the group means and group weights in the cell_based_long dataframe 
# and call this weighted_mean

# sum weighted means, grouping by question



```

## 2.2) Plot estimated means against benchmarks

```{r}
# merge mturk cell-based weighted estimates with benchmark


# plot (you can use the function we created above)


                
```

## 2.3) Plot distribution of estimation-benchmark differences

```{r}
#calculate difference

#plot


```


\newpage

# Approach 3: Means with post-stratification (160 groups) and missing group imputation

## 3.1) Calculate group means, group weights, and weighted means

Can you get better estimates grouping by more variables? Try grouping on sex, region, age group, and race. 

You will now have 160 groups (2 x 4 x 5 x 4). Some of groups may be missing from your sample (e.g. 50-64 year old black women in the midwest). If a group is missing, their answers will automatically be treated as "zero" when computing weighted means. As a result, some question responses may be underestimated. One way to deal with this is to impute the missing values with the sample average for that variable (aka the simple means we calculated in the first step). You will do this in the next step. 

First, calculate the new group means, group weights, and weighted means as you did above in Approach 2. We provide hints in comments to help you analze the data. 

```{r}
## Step 1: group population data by sex and region, age group and race
## To get group weight, get the sum for each cell and divide by total pop


## Step 2: check that weights sum to one

## Step 3: calculate group means for each question response

## Step 4: check how many empty cells there are

## Step 5: append group weights obtained from step 1 


```

### 3.1.1) Dealing with missing groups: imputing with sample means

Now, replace the missing groups with the sample means you computed in 1.1. 

```{r}
# replace missing group means with sample means




```

## 3.2) Plot estimated means against benchmarks

Plot both your new group means and the estimated means against the Pew benchmarks. 

```{r}
################################## WITH NO IMPUTATION ###################################
## Step 1: append benchmark estimate

## Step 2: generate the comparison graph from the first function we made


################################## WITH IMPUTATION ######################################
## Step 1: append benchmark estimate

## Step 2: generate the comparison graph from the first function we made


```


## 3.3) Plot distribution of estimation-benchmark differences

```{r}
#################################### WITH NO IMPUTATION #################################

#################################### IMPUTATION #######################################

```

\newpage
# Optional Extension -- Approach 4: Model-based estimation with post-stratification

## 4.1) Predict group means with simple regression model; combine with group weights to create weighted means

```{r}

```

## 4.2) Plot estimated means against benchmarks

```{r}

```

## 4.3) Plot distribution of estimation-benchmark differences 

```{r}

```


\newpage

# Compare distribution of differences across methods and questions

Which questions worked well and which didn't? Which methods worked well for which questions?

```{r}

```

\newpage

# Optional Extension: \
  Approach 5: Multilevel-Model-based estimation with post-stratification (MRP)

### 5.1) Predict group means with multi-level regression model; combine with group weights to create weighted means

```{r}

```

### 5.2) Plot estimated means against benchmarks

```{r}

```

### 5.3) Plot distribution of estimation-benchmark differences

```{r}

```

### 5.4) Compare differences from MRP with other methods

```{r}
