---
title: "Data Visualization Quiz"
author: "Summer Institutes in Computational Social Science"
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Additional Resources:** 

* [R4DS Chapters 17-21: Programming](https://r4ds.had.co.nz/program-intro.html)
* [R for Data Science Chapter 16: Dates and times](https://r4ds.had.co.nz/dates-and-times.html)


**Run the code below to load the `congress` dataframe we will use in this quiz** 

```{r message=FALSE, echo=TRUE}
load(url('https://dssoc.github.io/datasets/congress.RData'))
```
<br/>

## Questions
<br>


**1. In your own words, describe what a function is and provide one example of how you might use it in a data science 
<br/>


**2. Packages in R can contain many useful functions/commands. If you didn't know what a certain function did, or how it worked, where within RStudio would you look to learn more / see example code? Where would you look outside RStudio?**

<br/>


**3. Write a function that takes a character vector as an argument and returns a character vector containing the first letters of each element in the original vector. To show that it works, test it on the character vector `sentence` defined below.**
```{r}
sentence <- c('you', 'only', 'understand', 'data', 'if', 'data', 'is', 'tidy')
# your answer here
```
<br/>


**4. Create your own function which accepts a birthyear vector and returns an approximate current age, then use it on the `birthyear` column of the `congress` dataframe to create a new `age` column with `mutate`.**

Note: functions used inside mutate accept single columns from the original dataframe and return a column or vector of the same size. This is a valuable tool for developing your workflow.

<br/>


**5. Write a function that accepts a date string and returns the day of the week it corresponds to, then use it to create a new column of `congress` representing the weekday of the birth of each politician using `mutate`.**

<br/>


**6. Write a function that accepts a dataframe with the columns `birthday` and `full_name`, and prints the names and ages of the `k` oldest *representatives* in congress (i.e. not including senators) using a "for loop". In this sense, `k` is an arbitrary number that should be given as an argument to the function - set the default value to be 5. If you use the dataframe as the first argument, you can use the pipe operator ("%>%") to pass the dataframe directly to the function. Define your function such that you can use it like this: `congress %>% print_oldest(3)`.**

<br/>


**7. Starting with the function from the previous question, change it such that if k > 5, it only prints the first 5. Test isusing this code: `congress %>% print_oldest(100)`.**

<br/>

Thanks to Devin Cornell and Taylor Brown for helping to create these quizzes!


