---
title: "Office Network"
output: html_notebook
---

```{r Setup, include=FALSE}
pacman::p_load(tidyverse, igraph, tidygraph, ggraph,igraphdata,statnet,stargazer,intergraph,netrankr, viridis, schrute, ggsci,visNetwork)
```

Exercise:

- Get The Office transcript data by installing the schrute package.
- Convert the data to network format where a node is an actor and an edge connects two actors when they appear in the same episode.
- Calulate network level metrics for each season and plot it using ggplot and tables.
- Calculate node level metrics for each season and plot it using ggplot and tables.
- Bonus: Create a dynamic graph either using R, or by exporting the data to graphml (using `write.graph()`) and visualise in Gephi.

```{r echo=FALSE}
office <- schrute::theoffice %>% 
  filter(season ==1) %>%
  mutate(id = paste0(season,"_",episode)) %>% 
  select(id,season,episode, character,season) %>% 
  add_count(id,character, name = 'lines_in_episode') %>% 
  tidytext::cast_sparse(row = id,column = character,value = lines_in_episode) %>% 
  graph_from_incidence_matrix() %>% 
  bipartite_projection(which = TRUE) %>% 
  as_tbl_graph() %>% 
  mutate(group = factor(group_louvain()),
         value = centrality_degree())

nodes <- data.frame(office %>% data.frame() %>% rename('id' = name) %>% select(id,group,value))
nodes$font.size <-28

edges <- data.frame(get.edgelist(office %>% as.igraph()))
colnames(edges)<-c("from","to")

visNetwork(nodes, edges, height = "600px") %>%
  visIgraphLayout() %>%
  visNodes(size = 40) %>%
  visOptions(selectedBy = "group", 
             highlightNearest = TRUE, 
             nodesIdSelection = TRUE) %>%
  visInteraction(keyboard = TRUE,
                 dragNodes = T, 
                 dragView = T, 
                 zoomView = T)
```

