---
title: "Non-probability-based Surveys in Practice"
subtitle: "Warmup exercise 1"
author: "Bernhard Clemm von Hohenberg"
date: "7/25/2023"
output: html_document
---

# Load data 

```{r, message = F, warning = F, echo = T}

library(tidyverse)

dt <- read.csv("SICSS warmup-exercise-1.csv")
names(dt) <- c("timestamp", "height", "sex")
dt <- dt %>% mutate(height = as.numeric(height))

```

# Population mean

What is the average height in the population?

```{r, message = F, warning = F, echo = T}

mean(dt$height, na.rm = T)

```

# Probability-based (random) sample mean

What is the average height of a randomly drawn sample?

```{r, message = F, warning = F, echo = T}

dt_sample <- dt %>% slice_sample(prop = 0.66)
mean(dt_sample$height, na.rm = T)

```

What if we did this many times? The sampl*ing* average would be unbiased---that is, it would correspond to the population mean. In the figure below, the mean of the sampling distribution equals the population mean.

```{r, message = F, warning = F, echo = T}

sampling_df <- data.frame(
  sample_number = 1:500,
  sample_mean = NA)

for (i in 1:nrow(sampling_df)) {
  dt_sample <- dt %>% slice_sample(prop = 0.66)
  sampling_df[i, "sample_mean"] <- mean(dt_sample$height, na.rm = T)
}

sampling_df %>% ggplot(aes(x = sample_mean)) +
  geom_histogram() +
  geom_vline(xintercept = mean(sampling_df$sample_mean), color = "red") +
  geom_vline(xintercept = mean(dt$height), color = "blue") +
  scale_x_continuous(name = "Distribution of sample means") +
  theme_light()

```

# Non-random sample mean

Imagine that for some reason the subject recruitment is more likely to include males. What would be the likely sample mean? As male height on average differs from female height, it would likely be higher from the population mean.

```{r, message = F, warning = F, echo = T}

dt_sample_biased <- rbind(
  slice_sample(dt %>% filter(sex == "Male"), prop = 0.8),
  slice_sample(dt %>% filter(sex == "Female"), prop = 0.2))

mean(dt_sample_biased$height, na.rm = T)

```

Again, let's do this many times:

```{r, message = F, warning = F, echo = T}

biased_sampling_df <- data.frame(
  sample_number = 1:500,
  sample_mean = NA)

for (i in 1:nrow(biased_sampling_df)) {
  dt_sample_biased <- rbind(
    slice_sample(dt %>% filter(sex == "Male"), prop = 0.8),
    slice_sample(dt %>% filter(sex == "Female"), prop = 0.2))
  biased_sampling_df[i, "sample_mean"] <- mean(dt_sample_biased$height, na.rm = T)
}

biased_sampling_df %>% ggplot(aes(x = sample_mean)) +
  geom_histogram() +
  geom_vline(xintercept = mean(biased_sampling_df$sample_mean), color = "red") +
  geom_vline(xintercept = mean(dt$height), color = "blue") +
  scale_x_continuous(name = "Distribution of sample means") +
  theme_light()

```

The key question here is whether I *know* the inclusion probabilities (in this case, 0.8 for males and 0.2 for females). In this case, even though it is not a simple random sample, it is a probability-based sample. However, in practice I may not know the inclusion probabilities and have to *estimate* them!