---
title: "Spotify Example"
author: "Chris Bail"
date: "9/18/2018"
output: html_document
---

This is a brief tutorial designed to teach you how to collect data from Spotify in R. Though there are several packages for working with Spotify in R, they do not work very well and are not very well maintained. Therefore, we'll take this opportunity to write some more "raw" code that interfaces directly with the API instead of through a package. Much of this code is borrowed from Danielle Montagne- thanks Danielle!

# Getting information on Spotify's Global Top 50 chart

The example that we are going to work through is collecting a dataset that includes a large number of variables about the top 50 songs on Spotify worldwide right now. These include things like the artist's name, website, and markets where the music is being advertised.

First, we need to load the `httr` package and `dplyr` for making calls to the API and data wrangling, respectively

```{r}
library(httr)
library(dplyr)
```

Next, you need to set up your developer account here: https://developer.spotify.com/dashboard/ . You will be asked a series of questions about how you intent to use Spotify's API.

If your application is approved, you can view your "clientID"" and "secret" credentials from the main spotify developer console. Let's create two objects that describe these credentials as follows:

```{r}
clientID <- "YOURCLIENTIDHERE"
secret <- "YOURSECRETHERE"
```

First, we make a call to Spotify's "request API" which tells us whether or not we have permission to use the API using the `POST` function from the httr package: 

```{r}
response <- POST(
  'https://accounts.spotify.com/api/token',
  accept_json(),
  authenticate(clientID, secret),
  body = list(grant_type = 'client_credentials'),
  encode = 'form',
  verbose()
)
```

Next, we request an access token with our credentials:

```{r}
mytoken <- content(response)$access_token #extracting access token from the previous API Call
HeaderValue <- paste0('Bearer ', mytoken) #Authorization is always Bearer + unique token
```

query with desired endpoint to make API call - this is a 'playlist' call
This URL format can be broken apart and pasted back together in order to batch API calls. It is important to know the format of the endpoint you want to use, which determines what information you give and get a list of Spotify API endpoints can be found here: https://developer.spotify.com/documentation/web-api/reference/object-model/


```{r}
query <- paste0("https://api.spotify.com/v1/users/spotifycharts/playlists/37i9dQZEVXbMDoHDwVN2tF/tracks")
r <- GET(url = query, add_headers(Authorization = HeaderValue)) #The actual API call
r2 <- httr::content(r) #extracting the JSON information
```

This is where most of the music-related data is. Other parts of 'r2' have to do with rate limiting and success/failure status of the call

```{r}
items <- r2$items
```

Drom exploring the lists (within lists) of data within "items" we can see there is a lot of information you might want! But you also might not want all of it, and unlisting everything can create an unweidly dataset. The loop below creates an empty dataframe of the size we want to fill. For this example, we'll just extract the title of the song (name), the credited artist (artist), the track's unique spotify id (id, which can be used for future API calls), and the åsong's overall popularity on spotify (popularity, integer 0 - 100).

```{r}
global50 <- matrix(nrow= 50, ncol= 4)
global50<- as.data.frame(global50)
names(global50)<- c("name", "artist", "id", "popularity")

for (i in 1:50) {
  global50$name[i] <- items[[i]]$track$name
  global50$artist[i] <- items[[i]]$track$artists[[1]]$name
  global50$id[i] <- items[[i]]$track$id
  global50$popularity[i] <- items[[i]]$track$popularity
}
```

One can imagine that if you want many more variables (say, all of the available markets since this is chart is not limited to one country), this would not be a very efficient method. If we want all of the information this API call gives us for every track, we might want a different
method.

Since each song can have a different number of variables, we need to create an empty list to store a dataframe for each song. Thus, the list should be however many songs we have (50)

```{r}
complete_global50_list <- vector("list", length(items))
```

Then, we put each song's infromation into a dataframe, and store it in the list:

```{r}
for (i in 1:length(items)) {
  t <- unlist(r2$items[[i]], use.names = T)
  complete_global50_list[[i]] <- data.frame(lapply(t, type.convert), stringsAsFactors=FALSE) 
}
```

`complete_global50_list` is a list of dataframes, one for each song, which we now have to combine into one: note rbind.fill() appends datasets with different numbers of variables!

```{r}
complete_global50 <- plyr::rbind.fill(complete_global50_list)
```

This gives us a dataset of 50 observations, and 226 variables! The data are in wide-form, which is not usually the most useable format...
