\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{listings}
\usepackage{textcomp}
\lstset{language=Python,upquote=true,breaklines=true}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{wrapfig}
\usepackage{multicol}

\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt plus 1pt}
\setlength{\headheight}{13.6pt}
\newcommand\question[2]{\vspace{.25in}\hrule\textbf{#1: #2}\vspace{.5em}\hrule\vspace{.10in}}
\DeclareMathOperator{\Tr}{Tr}
\renewcommand\part[1]{\vspace{.10in}\textbf{(#1)}}
\newcommand{\exedout}{%
  \rule{0.8\textwidth}{0.5\textwidth}%
}
\pagestyle{fancyplain}
\lhead{\textbf{\NAME\ }}
\chead{\textbf{SICSS @ CU Boulder - Day 3: Network Analysis}}
\rhead{August 15, 2018}
\begin{document}\raggedright
\newcommand\NAME{Allie Morgan} 

\vspace{-0.2 in}
\question{1}{Fill out this short survey about Day 2: \href{https://goo.gl/forms/U4kigxnyhJg3qIKy1}{goo.gl/forms/U4kigxnyhJg3qIKy1}} 
\vspace{1 in}

\question{2}{What's your working definition or previous exposure to network analysis? What do you think are the opportunities and limitations?}
With your neighbor, discuss how you are using, or plan to use, network science for your research.
\begin{itemize}
\item What networks are you examining? 
\item How was this network constructed? 
\item What are the nodes and links? 
\item Is it temporal? Are the edges weighted or unweighted? Is the network bipartite? 
\item How does this data structure allow for different analyses than time series or traditional survey data sources?
\end{itemize}

\end{document}
