---
title: "Answers for HW from Day 2"
author: "Maria Y. Rodriguez"
date: "6/20/2018"
output: 
  beamer_presentation:
      theme: "Madrid"
      colortheme: "default"
      fonttheme: "professionalfonts"
---
# Overview

This Rmd file contians code chunks to answer the hw questions. 
Run it in your own Rstudio session to visualize results. 

# A Sample Analysis - Answers 

1. Calculate the mode for all variables 

```{r eval=FALSE}
# Create the function
data(mtcars)
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
getmode(mtcars$mpg)
getmode(mtcars$disp)
getmode(mtcars$hp)
getmode(mtcars$hp)

#trick question - some of these are factors!
getmode(mtcars$cyl)
```
# A Sample Analysis - Answers 

2. Examine correlations between all variables (bonus if you do it with a graph)

```{r eval=FALSE}
data(mtcars)
install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")
my_data <- mtcars[, c(1,3,4,5,6,7)]
chart.Correlation(my_data, histogram=TRUE, pch=19)
```
# A Sample Analysis - Answers 

3. Run a linear regression with mpg as the dependent variable and 3 independent          variables 

```{r eval=FALSE}
fitted_lm = lm(mpg ~ wt+disp+hp, data = mtcars)
summary(fitted_lm)
```
# A Sample Analysis - Answers 

4. Recreate this next graph 
```{r eval=FALSE}
data(mtcars)
library(ggplot2)
ggplot(mtcars, aes(hp, mpg)) + geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  ylab("Miles per Gallon") +
  xlab("No. of Horsepower") +
  ggtitle("Impact of Number of Horsepower on MPG")
```