---
title: "Hunter SiCSS Day 2"
author: "Maria Y. Rodriguez"
date: "6/19/2018"
output: 
  beamer_presentation:
      theme: "Madrid"
      colortheme: "default"
      fonttheme: "professionalfonts"
---
# Overview 

1. Review from Yesterday 
2. Getting started with R: Version Control
  - connecting git to GitHub
  - connecting Git + Github to Rstudio 
3. A Sample Analysis   

# Review from Yesterday 

What we've learned so far: 
 1. R is great! And annoying!
 
 2. Stuff we can do in R:  
  - install packages 
  - load packages 
  - create directories 

Where we left off: 

Git! 

# Connect Git to GitHub
Source: http://happygitwithr.com/push-pull-github.html

1. Make a repository on Github:
  - make public 
  - YES initialize README.md
  
2. Clone repository to your local computer using terminal

```{r eval=FALSE}
git clone 
https://github.com/YOUR-USERNAME/YOUR-REPOSITORY.git
```

# Connect Git to GitHub
Source: http://happygitwithr.com/push-pull-github.html

3. Make repository the working directory using terminal 
```{r eval=FALSE}
cd myrepo
ls
head README.md
git remote show origin
```

# Connect Git to GitHub
Source: http://happygitwithr.com/push-pull-github.html

4. Make a local change to your file 
```{r eval=FALSE}
echo "A line I wrote on my local computer" >> README.md
git status
```

# Connect Git to GitHub
Source: http://happygitwithr.com/push-pull-github.html

5. Commit change from local to github

You'll be asked for your pw: this could get tricky!!
```{r eval=FALSE}
git add -A
git commit -m "A commit from my local computer"
git push
```

# Connect Git to GitHub
Source: http://happygitwithr.com/push-pull-github.html

6. Confirm you did it

Go back to Github.com. Make sure you're in your repository. 

Refresh.

You should see the new “A line I wrote on my local computer” in the README.

# Connect Git and Github
Source: http://happygitwithr.com/push-pull-github.html

If you don't want to put in your password everytime: 

1. Use the same repo you were working with 

```{r eval=FALSE}
git remote -v
git branch -vv
git --version
#need version 1.7 or better 
git credential-osxkeychain
```

# Connect Git and Github
Source: http://happygitwithr.com/push-pull-github.html

If you don't want to put in your password everytime: 

1. Use the same repo you were working with 

```{r eval=FALSE}
git config --global credential.helper osxkeychain
#trigger a pw challenge 
echo "adding a line" >> README.md
git add -A
git commit -m "A commit from my local computer"
git push -u origin master
#enter pw
git push
```

# Connect Git + Github to Rstudio 
Source: http://happygitwithr.com/push-pull-github.html

To connect git + github + Rstudio 
```{r eval=FALSE}
File > New Project > Version Control > Git> Create Project
```
In the “repository URL” paste the URL of your sample GitHub repository. 
It will be something like this https://github.com/jennybc/myrepo.git.
You should now have the README.md file in your git tab in Rstudio. 

# Connect Git + Github to Rstudio 
Source: http://happygitwithr.com/push-pull-github.html

From RStudio, modify the README.md file, e.g., by adding the line 
“This is a line from RStudio”. Save your changes.

From RStudio:

Click the “Git” tab in upper right pane.
Check “Staged” box for README.md.
If you’re not already in the Git pop-up, click “Commit”.
Type a message in “Commit message”, such as “Commit from RStudio”.
Click “Commit”.
Click the green “Push” button to send your local changes to GitHub.

# Connect Git + Github to Rstudio 
Source: http://happygitwithr.com/push-pull-github.html

Confirm you did it

Go back to Github.com. Make sure you're in your repository. 

Refresh.

You should see the new “This is a line from Rstudio” in the README.

# A Sample Analysis 

Create a new project called "Sample Analysis"
Make sure version control is enabled. 

```{r, eval=FALSE}
#Let's run through a sampele analysis of a built in R dataset
data("mtcars")
#Find out more about the dataset
?mtcars
#dataset structure
str(mtcars)
#first 5 observations
head(mtcars)
```

# A Sample Analysis Continued

```{r, eval=FALSE}
#last 5 observations
tail(mtcars)
# Number of rows (observations)
nrow(mtcars)
# Number of columns (variables)
ncol(mtcars)
#variable names 
names(mtcars)
#descriptive stats for each variable 
summary(mtcars)
```

# A Sample Analysis 

Using the Quick R website (https://www.statmethods.net/) complete the following: 

1. Calculate the mode for all variables 
2. Examine correlations between all variables (bonus if you do it with a graph)
3. Run a linear regression with mpg as the dependent variable and 3 independent          variables 
4. Recreate this next graph 

# A Sample Analysis: Recreate this graph  

```{r mtcars, echo=FALSE}
library(ggplot2)
ggplot(mtcars, aes(hp, mpg)) + geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  ylab("Miles per Gallon") +
  xlab("No. of Horsepower") +
  ggtitle("Impact of Number of Horsepower on MPG")
```