---
title: "Non-probability-based Surveys in Practice"
subtitle: Analysis template
author: Bernhard Clemm von Hohenberg ^[based on the activities from SICSS 2019 (Matthew Salganik and Cambria Naslund).]
date: "Summer Institute in Computational Social Science 2023" 
output:
  html_document:
    df_print: paged
    toc: yes
---

```{r, echo=F}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# packages
library(tidyverse)
library(caret)

# set working directory (not necessary if you work in RMD)
# setwd("")

```

# Load packages and data

If you are using your own survey data, you will need to do some pre-processing as described in `preprocessing-template.Rmd`.

```{r, message = F, warning = F, echo = T }

# read in pre-processed simulated data file
prolific <- read.csv("data-simulated/survey-simulated-clean.csv")

# read in census data
census <- read.csv("data-census/census-2021-cleaned.csv", sep = ";")
## as our target population are adults, we drop <18 year olds
census <- census %>%
  filter(age_group != "<18")

# load Eurobarometer benchmarks
eb_means <- read.csv("data-eurobarometer/eb99_2023_means.csv", sep = ";")
eb_means <- eb_means %>% 
  select(varname_sicss, proportion) %>%
  rename("estimate_eb" = proportion)
```

\newpage

# Approach 1: Simple means 

First, we'll just take the mean of the whole sample for each question. This approach doesn't use any post-stratification.

## 1.1 Calculate means

```{r}
# take the mean of survey responses in Prolific data
prolific_means <- prolific %>% select(-c(
  "timestamp", "consent", "prolific_id", "age", "sex", "residence",
  "education", "party", "age_group")) %>%
  summarise_all(~mean(., na.rm = T))

# reshape from wide to long
## call question column "varname_sicss", same as in EB data, and mean
prolific_means <- prolific_means %>% 
  gather(varname_sicss, mean)

# preview
head(prolific_means)
```

## 1.2) Plot estimated means against benchmarks

As you will be making this type of plot each time you generate a new set of estimates, we wrap the plotting in a function.

```{r}

# merge Prolific mean estimates with Eurobarometer benchmark
mean_est <- inner_join(
  eb_means, 
  prolific_means, by = c("varname_sicss"))

# make function for plot
plot_comparison <- function(est_table, method, caption){
  graph <-  ggplot(est_table, 
                   aes(x = estimate_eb, y = method)) + 
  geom_point() + 
  labs(x = "Estimates from Eurobarometer", y = caption) +
  scale_x_continuous(limits = c(0,1)) + 
  scale_y_continuous(limits = c(0,1)) + 
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") + 
  coord_fixed() +
  theme_bw()
  return(graph)
}  

# plot
plot_comparison(
  est_table = mean_est, 
  method = mean_est$mean, 
  caption = "Non-weighted estimates from Prolifc")

```

## 1.3) Plot distribution of estimation-benchmark differences 

Again, as you will be making this type of plot each time you generate a new set of estimates, we wrap the plotting in a function.

```{r}

# calculate difference
mean_est$diff <- abs(mean_est$mean - mean_est$estimate_eb)

# function for plotting difference
plot_diff <- function(est_table){
  diff_graph <- ggplot(est_table, aes(x = diff)) + 
  geom_histogram(binwidth = .025, 
                 colour = "black", fill = "white")  + 
  geom_vline(aes(xintercept = median(diff)), linetype = "longdash") + 
  labs(x = "absolute difference", y = "density") + 
  theme_bw()
  return(diff_graph)
}

# plot
plot_diff(mean_est)


```

\newpage

# Approach 2: Means with post-stratification (8 groups)

## 2.1) Calculate group means, group weights, and weighted means

To start, group by sex and age group only. This should give you 8 groups (2 sexes by 4 age groups). Group weights can be calculated as $\frac{N_{h}}{N}$. They should sum to 1. You will need to calculate these group weights for the other approaches as well. 

```{r}

# get total census population
N <- sum(census$POP)

# calculate group weights 
population_counts <- census %>% 
  group_by(sex, age_group) %>%
  summarise(group_weight = sum(POP)/N)

# check that weights sum to one
if (sum(population_counts$group_weight) != 1) {print("weights don't sum to 1")}

# calculate group means for each question response
sample_counts <- prolific %>%
  group_by(sex, age_group) %>% 
  select(-c("timestamp", "consent", "prolific_id", "age", "residence",
            "education", "party")) %>%
  summarise_all(list(~mean(.,na.rm = T)))

# check that there are no empty cells
if (nrow(sample_counts) < nrow(population_counts)) {
  print("GROUPS MISSING:")
  print(nrow(population_counts) - nrow(sample_counts))
}

# merge population counts with sample counts
cell_based <- left_join(
  population_counts, 
  sample_counts, 
  by = c("sex", "age_group"))

# reshape to long
cell_based_long <- cell_based %>% 
  gather(varname_sicss, mean, -c(sex, age_group, group_weight), na.rm = F)

# multiply the group means and group weights 
cell_based_long <- cell_based_long %>%
  mutate(weighted_mean = group_weight*mean)

# sum weighted means, grouping by question
prolific_cell_est <- cell_based_long %>% 
  group_by(varname_sicss) %>%
  summarise(cell_estimate = sum(weighted_mean, na.rm = T))

head(prolific_cell_est)
```

## 2.2) Plot estimated means against benchmarks

```{r}
# merge Eurobarometer cell-based weighted estimates with benchmark
cell_est <- inner_join(
  eb_means, 
  prolific_cell_est, 
  by = c("varname_sicss"))

# plot (you can use the function we created above)
plot_comparison(
  est_table = cell_est, 
  method = cell_est$cell_estimate, 
  caption = "Cell-weighted estimates from Prolific")

```

## 2.3) Plot distribution of estimation-benchmark differences

```{r}

#calculate difference

#plot

```

\newpage

# Approach 3: Means with post-stratification (160 groups) and missing group imputation

## 3.1) Calculate group means, group weights, and weighted means

Can you get better estimates grouping by more variables? Try grouping on sex, age group anbd region. You will now have 64 groups (2 x 4 x 8). Some of groups may be missing from your sample (e.g. 65+ women in Yorkshire). If a group is missing, their answers will automatically be treated as "zero" when computing weighted means. As a result, some question responses may be underestimated. 

One way to deal with this is to impute the missing values with the sample average for that variable (aka the simple means we calculated in the first step). You will do this in the next step. 

First, calculate the new group means, group weights, and weighted means as you did above in Approach 2. 

```{r}

# calculate group means, group weights, and weighted means


```

### 3.1.1) Dealing with missing groups: imputing with sample means

Now, replace the missing groups with the sample means you computed in 1.1. 

```{r}

# replace missing group means with sample means

```

## 3.2) Plot estimated means against benchmarks

Plot both your new group means and the estimated means against the Pew benchmarks. 

```{r}

################################## WITH NO IMPUTATION ###################################


################################## WITH IMPUTATION ######################################


```


## 3.3) Plot distribution of estimation-benchmark differences

```{r}

#################################### WITH NO IMPUTATION #################################


#################################### IMPUTATION #######################################


```

\newpage

# Approach 4: Model-based estimation with post-stratification

## 4.1) Predict group means with simple regression model; combine with group weights to create weighted means

```{r}


```

## 4.2) Plot estimated means against benchmarks

```{r}


```

## 4.3) Plot distribution of estimation-benchmark differences 

```{r}



```


\newpage

# Compare distribution of differences across methods and questions

Which questions worked well and which didn't? Which methods worked well for which questions?

```{r}


```

\newpage